\documentclass{my_cv}

\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage[letterpaper, margin=1in]{geometry}

\begin{document}

\name{Ryan Luu}
\contact{Stockton, CA}{hi@ryanluu.dev}{\href{tel:12097749521}{+1 (209) 774-9521}}

\section{Education}

\datedsubsection{Middle College High School}{Aug 2022 -- May 2026}
\begin{itemize}
    \item Led the community Discord server for my year
\end{itemize}

\datedsubsection{San Joaquin Delta College}{Aug 2022 -- May 2026}

\section{Work}

\datedsubsection{Boba \& Rolls}{Jan 2025 -- Present}
\begin{itemize}
    \item Managed website development, branding, social media, and IT infrastructure
\end{itemize}

\datedsubsection{San Joaquin County Registrar of Voters}{Nov 2024}
\begin{itemize}
    \item Went through training on how to run a voting booth
    \item Handled answering voter concerns and questions
    \item Operated ballot scanner and submitted mail in ballots
\end{itemize}

\section{Volunteering}

\datedsubsection{Verizon Innovative Learning}{Oct 2024 -- Jul 2025}
Helped to teach middle school students at Verizon Innovative Learning on San Joaquin Delta College's campus. Took supervisory roles over the supervision of the students along with the setup and cleanup of activities. Assisted teachers in learning by answering questions, setting up classrooms, and other miscellaneous things.

\datedsubsection{Roblox Research Panel}{Sep 2023 -- Present}
Member of the Roblox Research Panel, an exclusive invite-only program where people can share their opinions and insights to help improve Roblox. Participated in several types of research including surveys, polls, discussions, and testing. Provided essential feedback to Roblox.

\datedsubsection{Science Olympiad}{Oct 2023 -- Mar 2025}
Performed weekly online meetings, assigned and graded homework, studied rules and materials to best assist my students. My goal was to teach students and make sure they were on track to Science Olympiad including handling communication between students, parents, and other coaches. Taught the codebusters and fast facts events from Science Olympiad.

\datedsubsection{BigFuture Ambassador}{Sep 2025 -- Present}
Collaborated with my school's teachers and counselor to better spread awareness for college and career readiness with the resources provided to me from BigFuture on a weekly basis to meet the ambassador roadmap. Assisted classmate with using the BigFuture website and promoting relevant tooling.

\section{Skills}
\begin{tabular}{l l l l}
C\# & Luau & JavaScript & GitHub \\
Customer Service & Communication
\end{tabular}

\end{document}
